### 2015-11-27 Irregular-occ/Irregular-occ.tex
.

\begin{figure*}
\begin{centering}
\subfigure[Prediction with STE ephemeris]{\includegraphics[width=8.8cm]{figures/Himalia_STE.eps}  \label{Fig: occ-Himalia-STE}}
\subfigure[Prediction with JPL ephemeris]{\includegraphics[width=8.8cm]{figures/Himalia_JPL.eps}  \label{Fig: occ-Himalia-JPL}}
\subfigure[Observation at February 22 (different FOVs)]{\includegraphics[width=8.8cm]{figures/Himalia_22fev.eps}   \label{Fig: occ-Himalia-off22fev}}
\subfigure[Observation at March 03 (same FOV)]{\includegraphics[width=8.8cm]{figures/Himalia_03mar.eps}   \label{Fig: occ-Himalia-off03mar}}
\caption{Predictions for Himalia: The straight lines show the size of the shadow. The big red dot show the geocentric closest approach of the shadow. The black "+" marks at maps (b,c,d) are the STE prediction closest approach for reference. The small red ones are the center of the shadow separated by one minute. \ref{Fig: occ-Himalia-STE} is the map using the STE ephemeris showed in Sec. \ref{Sec: integration}. \ref{Fig: occ-Himalia-JPL} shows the shadow using the JPL ephemeris. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. The green dot at the bottom of the maps is the location of Observatório do Pico dos Dias.}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

\begin{figure*}
\begin{centering}
\includegraphics[width=17.6cm]{figures/HIMALIA.eps}
\caption{TESTE DE MAPA. STE = AZUL, JPL=VERMELHO, 22FEV=PRETO, 03MAR=VERDE%Predictions for Himalia: The straight lines show the size of the shadow. The big red dot show the geocentric closest approach of the shadow. The black "+" marks at maps (b,c,d) are the STE prediction closest approach for reference. The small red ones are the center of the shadow separated by one minute. \ref{Fig: occ-Himalia-STE} is the map using the STE ephemeris showed in Sec. \ref{Sec: integration}. \ref{Fig: occ-Himalia-JPL} shows the shadow using the JPL ephemeris. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. The green dot at the bottom of the maps is the location of Observatório do Pico dos Dias.
}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

@@

\begin{table}
\caption{\label{Tab: comparison-Himalia} Comparison between the predictions of the Himalia occultation at March 03, 2015.}
\begin{centering}
\begin{tabular}{lccc}
\hline  \hline
\multicolumn{4}{c}{Difference from STE prediction} \tabularnewline
Method  & Instant of C/A  & C/A & Map   \tabularnewline
\hline
STE & 00:39:51 UTC & $0\farcs703$ & \ref{Fig: occ-Himalia-STE} \tabularnewline
JPL & -26s & +11mas (36km) & \ref{Fig: occ-Himalia-JPL} \tabularnewline % (284km)
Feb. 22 Obs. & -14s & -20mas (65km) & \ref{Fig: occ-Himalia-off22fev} \tabularnewline % (153km)
Mar. 03 Obs. & -36s & -09mas (29km) & \ref{Fig: occ-Himalia-off03mar} \tabularnewline % (393km)
\hline
\end{tabular}
\par\end{centering}
%*Closest Approach
\end{table}

>>>>

%\begin{figure*}
%\begin{centering}
%\subfigure[Prediction with STE ephemeris]{\includegraphics[width=8.8cm]{figures/Himalia_STE.eps}  \label{Fig: occ-Himalia-STE}}
%\subfigure[Prediction with JPL ephemeris]{\includegraphics[width=8.8cm]{figures/Himalia_JPL.eps}  \label{Fig: occ-Himalia-JPL}}
%\subfigure[Observation at February 22 (different FOVs)]{\includegraphics[width=8.8cm]{figures/Himalia_22fev.eps}   \label{Fig: occ-Himalia-off22fev}}
%\subfigure[Observation at March 03 (same FOV)]{\includegraphics[width=8.8cm]{figures/Himalia_03mar.eps}   \label{Fig: occ-Himalia-off03mar}}
%\caption{Predictions for Himalia: The straight lines show the size of the shadow. The big red dot show the geocentric closest approach of the shadow. The black "+" marks at maps (b,c,d) are the STE prediction closest approach for reference. The small red ones are the center of the shadow separated by one minute. \ref{Fig: occ-Himalia-STE} is the map using the STE ephemeris showed in Sec. \ref{Sec: integration}. \ref{Fig: occ-Himalia-JPL} shows the shadow using the JPL ephemeris. In \ref{Fig: occ-Himalia-off22fev} we apply offsets to the positions of star and satellite accordingly the observations made at February 22. \ref{Fig: occ-Himalia-off03mar} is as in \ref{Fig: occ-Himalia-off22fev} but with observations made at March 03 when the objects were close to each other. The green dot at the bottom of the maps is the location of Observatório do Pico dos Dias.}
%\label{Fig: occ-Himalia}
%\end{centering}
%\end{figure*}

\begin{figure*}
\begin{centering}
\includegraphics[width=17.6cm]{figures/HIMALIA.eps}
\caption{Predictions for Himalia: The straight lines show the center of the shadow over time. In blue is for the prediction using the STE ephemeris showed in Sec. \ref{Sec: integration}. In red the shadow using the JPL ephemeris. In black we apply offsets to the positions of star and satellite accordingly the observations made at February 22. In green, the same for the previous one but with observations made at March 03 when the objects were close to each other. The dots show the closest approach of the shadow for each prediction.}
\label{Fig: occ-Himalia}
\end{centering}
\end{figure*}

@@

\begin{table}
\caption{\label{Tab: comparison-Himalia} Comparison between the predictions of the Himalia occultation at March 03, 2015.}
\begin{centering}
\begin{tabular}{lcc}
\hline  \hline
\multicolumn{3}{c}{Difference from STE prediction} \tabularnewline
Method  & Instant of C/A  & C/A   \tabularnewline
\hline
STE & 00:39:51 UTC & $0\farcs703$ \tabularnewline
JPL & -26s & +11mas (36km) \tabularnewline % (284km)
Feb. 22 Obs. & -14s & -20mas (65km) \tabularnewline % (153km)
Mar. 03 Obs. & -36s & -09mas (29km) \tabularnewline % (393km)
\hline
\end{tabular}
\par\end{centering}
%*Closest Approach
\end{table}
